Bayesian exponential random graph modelling of KWL Burial network

### 2020-03-29 analysis/paper/paper.Rmd
add implication of gwdegree

3. gwdegree (geometrically weighted degree distribution): a parametric form that represents the frequency distribution for nodal degree, each node counts only once. The local configuration is degrees and stars that are equivalent representations for the distribution of node-based edge counts

@@

```{r model-ergm-2}
model.2 <- burial_network_pre ~ edges + # density
  gwesp(0.2, fixed = TRUE) +  # transitivity(cohesion; triangle), a tendency for those with shared partners to become tied, or tendency of ties to cluster together
  # triad-based clustering according to dyad-based configurations instead of node-based
  # number means weight parameter alpha, which controls the rate of declining marginal returns
  # fixed = TRUE means the scale parameter lambda is fit as a curved exponential-family model
  # not much difference in a range of 0-1.5, the lower the value of the scaling parameter, the less likely the model is to be degenerate
  # ergm can estimate the parameter from the data by using fixed=FALSE
  # http://mailman13.u.washington.edu/pipermail/statnet_help/2010/000575.html
  gwdegree(0.8, fixed = TRUE)  # popularity(degree; star), the frequency distribution for nodal degrees
  # tendency of being in contact with multiple partners, measures of centralisation
  # distribution of node-based edge counts, each node counts only once
  # number means weight parameter decay
  # Morris et al. (2008)
summary(model.2)
```

@@

θ1 = number of ties
θ2 = individuals with the same abundance of burial goods
θ3 = gwesp is negative that rejects the assumption that actors with multiple partners in common are more likely to be directed connected
θ4 =

>>>>

3. gwdegree (geometrically weighted degree distribution): a parametric form that represents the frequency distribution for nodal degree, each node counts only once. The local configuration is degrees and stars that are equivalent representations for the distribution of node-based edge counts. A measure of the tendency of the number of edges into a node. gwdegree estimates the change in tie likelihood given the degree of the nodes involved, but with marginally decreasing weighting as degree increases(https://www.r-bloggers.com/ergm-tutorial/). This statistic captures the tendency towards centralisation in the degree distribution of the network.

@@

```{r model-ergm-2}
model.2 <- burial_network_pre ~ edges + # density
  gwesp(0.2, fixed = TRUE) +  # transitivity(cohesion; triangle), a tendency for those with shared partners to become tied, or tendency of ties to cluster together
  # triad-based clustering according to dyad-based configurations instead of node-based
  # number means weight parameter alpha, which controls the rate of declining marginal returns
  # fixed = TRUE means the scale parameter lambda is fit as a curved exponential-family model
  # not much difference in a range of 0-1.5, the lower the value of the scaling parameter, the less likely the model is to be degenerate
  # ergm can estimate the parameter from the data by using fixed=FALSE
  # http://mailman13.u.washington.edu/pipermail/statnet_help/2010/000575.html
  gwdegree(0.8, fixed = TRUE)  # popularity(degree; star), the frequency distribution for nodal degrees
  # tendency of being in contact with multiple partners, measures of centralisation
  # distribution of node-based edge counts, each node counts only once
  # number means weight parameter decay
  # Morris et al. (2008)
  # The closer decay is to zero, the more gwdegree considers low degree nodes relative to high degree nodes
summary(model.2)
```

@@

θ1 = number of ties
θ2 = individuals with the same abundance of burial goods
θ3 = gwesp, a positive sign suggests a tendency of burials in our sample to group together in closed transitive structures. In mortuary context, clustering implies a tendency of burials with the same status indicated by prestige goods to be organised in closed structures. Burials with multiple prestige goods in common are more likely to be directed connected.
θ4 = gwdegree, negative estimates reflect an increased likelihood on ties to higher-degree nodes, or the strong edges are not necessarily centralised or dispersed in the degree distribution.
